---
title: "Museum_Boards_R"
output: html_document
date: "2023-11-08"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

library(tidyverse)


Museum_participants <- read_csv("/Users/Nwood/OneDrive - J. Paul Getty Trust/Collectors_MuseumBoard.csv", col_names = TRUE, col_types = cols(.default = "c"))

Museum_roles <- read_csv("/Users/Nwood/OneDrive - J. Paul Getty Trust/MuseumBoard_Roles.csv", col_names = TRUE, col_types = cols(.default = "c"))

Museum_sectors <- read_csv("/Users/Nwood/OneDrive - J. Paul Getty Trust/Collectors_MuseumBoards_Sectors.csv", col_names = TRUE, col_types = cols(.default = "c"))

#nodes

gephi_nodes1 <- Museum_participants %>%
  select(label = Name) %>%
  mutate(category = "collector")

gephi_nodes2 <- Museum_roles %>%
  select(label = Organization) %>%
  distinct(label) %>%
  mutate(category = "museum")
  
gephi_nodes_museum <- bind_rows(gephi_nodes1, gephi_nodes2)

gephi_nodes_museum <- gephi_nodes_museum %>%
  mutate(id = row_number())

#edges

gephi_edges_museum <- Museum_roles %>%
  select(source_label = Name,
  target_label = Organization)

#creating edges df with distinct connections

gephi_edges_museum_distinct <- gephi_edges_museum[!duplicated(gephi_edges_museum),]

gephi_edges_museum_distinct <- gephi_edges_museum_distinct %>%
  left_join(gephi_nodes_museum, by = c("source_label" = "label"))
  
gephi_edges_museum_distinct <- gephi_edges_museum_distinct %>%
  mutate(source = id,
    source_category = category) %>%
  select(-id,
    -category)
    
```{r}
gephi_edges_museum_distinct <- gephi_edges_museum_distinct %>%
  left_join(gephi_nodes_museum, by = c("target_label" = "label"))
```

```{r}
gephi_edges_museum_distinct <- gephi_edges_museum_distinct %>%
  mutate(target = id,
         target_category = category) %>%
  select(-id,
         -category)
```

```{r}
write_csv(gephi_nodes_museum, "/Users/Nwood/OneDrive - J. Paul Getty Trust/gephi_nodes_museum.csv")
write_csv(gephi_edges_museum_distinct, "/Users/Nwood/OneDrive - J. Paul Getty Trust/gephi_edges_museum_distinct.csv")
```

#sectors of museum participants

```{r}
gephi_node3 <- Museum_sectors %>%
  select(label = Sector) %>%
  distinct(label) %>%
  mutate(category = "Sector")
```

```{r}
gephi_nodes_sector <- bind_rows(gephi_nodes1, gephi_node3)
```

```{r}
gephi_nodes_sector <- gephi_nodes_sector %>%
  mutate(id = row_number())
```

```{r}
sector_edges <- Museum_sectors %>%
  select(source_label = Name,
         target_label = Sector)

sector_edges_distinct <- sector_edges[!duplicated(sector_edges),] %>%
  drop_na(target_label)
```

```{r}
sector_edges_distinct <- sector_edges_distinct %>%
  left_join(gephi_nodes_sector, by = c("source_label" = "label"))
```

```{r}
sector_edges_distinct <- sector_edges_distinct %>%
  mutate(source = id, 
         source_category = category)
```

```{r}
sector_edges_distinct <- sector_edges_distinct %>%
  select(-id,
         -category)
```

    ```{r}
sector_edges_distinct <- sector_edges_distinct %>%
      left_join(gephi_nodes_sector, by = c("target_label" = "label"))
    
sector_edges_distinct <- sector_edges_distinct %>%
  mutate(target = id,
         target_category = category) %>%
  select(-id,
         -category)
```

#adding museum role to as a node variable 

```{r}
gephi_nodes_sector_museumrole <- gephi_nodes_sector %>%
  left_join(Museum_roles, by = c("label" = "Name"))

gephi_nodes_sector_museumrole <- gephi_nodes_sector_museumrole %>%
  select(-Title, -Source)

gephi_nodes_museums <- gephi_nodes_sector_museumrole %>%
  select(-Title_Simple)

gephi_nodes_museums_distinct <- gephi_nodes_museums[!duplicated(gephi_nodes_museums),]

write_csv(sector_edges_distinct, "/Users/Nwood/OneDrive - J. Paul Getty Trust/gephi_sector_edges_distinct.csv")
write_csv(gephi_nodes_museums_distinct, "/Users/Nwood/OneDrive - J. Paul Getty Trust/gephi_nodes_museum_distinct.csv")
```

#adding museum org as an edge variable

```{r}
#fixing duplicate node IDs (because collectors served on boards at more than 1 museum)
gephi_nodes_museums_distinct[3, "Organization"] <- "Metropolitan Museum of Art and Brooklyn Museum of Art"
gephi_nodes_museums_distinct[12, "Organization"] <- "Metropolitan Museum of Art and Brooklyn Museum of Art"

gephi_nodes_museums_distinct <- gephi_nodes_museums_distinct[-4,]
gephi_nodes_museums_distinct <- gephi_nodes_museums_distinct[-12,]
```

```{r}
sector_edges_distinct <- sector_edges_distinct %>%
  left_join(gephi_nodes_museums_distinct, by = c("source_label" = "label"))

sector_edges_distinct <- sector_edges_distinct %>%
  select(-id)

write_csv(sector_edges_distinct, "/Users/Nwood/OneDrive - J. Paul Getty Trust/gephi_sector_museum_edges_distinct.csv")
```

